Sampling in Decisions from Experience

### 2022-01-20 talk-modelers-meeting/slides_modelers-meeting.Rmd
Add slides from modelers' meeting talk

---
title: "Sampling in Decisions from Experience"
subtitle: https://github.com/linushof/sampling-in-dfe
author: "Linus, Veronika & Thorsten"
date: "October 11, 2021"
output:
  beamer_presentation: default
bibliography: references_sampling-in-dfe.bib
csl: apa.csl
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, 
               scico,
               ggpubr)
```

@@

1. Description-experience gap [cf. @wulffMetaanalyticReviewTwo2018]

@@

- Hills and Hertwig [-@hillsInformationSearchDecisions2010]: Assumption of a systematic link between sampling and decision strategies

@@

```{r, echo=FALSE, out.height="40%", out.width="40%", fig.align='center'}
knitr::include_graphics("hills-hertwig_2010_figure-1.png")
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
cols <- list(.default = col_double(),
             boundary = col_factor(),
             a = col_factor(),
             parameter = col_factor())
cpt <- read_csv("data/estimates/estimates_cpt.csv", col_types = cols)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
cols <- list(.default = col_double(),
             boundary = col_factor(),
             gamble = col_factor(),
             rare = col_factor(),
             agent = col_factor(),
             choice = col_factor())
choices <- read_csv("data/choices/choices.csv", col_types = cols)

@@

## References

>>>>

---
title: "Sampling in Decisions from Experience"
subtitle: https://github.com/linushof/sampling-in-dfe
author: "Linus, Veronika & Thorsten"
date: "October 11, 2021"
output:
  beamer_presentation: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, 
               scico,
               ggpubr,
               here)
```

@@

1. Description-experience gap [cf. Wulff et al. 2018](https://doi.org/10.1037/bul0000115)

@@

- [Hills and Hertwig (2010)](https://doi.org/10.1177/0956797610387443): Assumption of a systematic link between sampling and decision strategies

@@

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}

cols <- list(.default = col_double(),
             boundary = col_factor(),
             a = col_factor(),
             parameter = col_factor())
cpt <- read_csv(here("data", "estimates", "estimates_cpt.csv"), col_types = cols)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
cols <- list(.default = col_double(),
             boundary = col_factor(),
             gamble = col_factor(),
             rare = col_factor(),
             agent = col_factor(),
             choice = col_factor())
choices <- read_csv(here("data", "choices", "choices.csv"), col_types = cols)

@@
